\documentclass[11pt,a4paper,sans]{moderncv} 
\usepackage{hyperref}
\moderncvcolor{blue}                              
\usepackage[utf8]{inputenc}                       
 \usepackage[left=2cm, right=2cm, top=1.7cm]{geometry}

\usepackage{import}


\name{FIROJ AHMMED}{PATWARY} 

\address{Oberfeldstr. 132, 12683, Berlin, Germany}
\phone[mobile]{+491729538112}      
\email{firoj.stat@gmail.com}                              
\social[github]{firojap}
\social[linkedin]{firojap}
\homepage{www.firoj.net}
\social[twitter]{firoj\_sajeeb}
\begin{document}

\makecvtitle 
\vspace{-15pt}
Affective Computing, Neural Networks, Healthcare Analytics, Data Mining \& Big Data Analytics,
Recommender Systems, Educational Technology, and Natural Language Processing.\\


\section{EXPERIENCES}

\vspace{4pt}

\begin{itemize}

\item{\cventry{July 2018 -- September 2019}{www.insightintechnology.com}{Junior Data Scientist}{InsightIn Technology Bangladesh}{}{\vspace{3pt} 
\begin{itemize}
\item Worked Closely with a strategy data-driven team and stakeholders on various projects for automation.
\item Contribute to different projects related to machine learning, data visualization, performance analysis and perform various statistical tests.
\item Collection data from different sources writing web crawler.
\end{itemize}
}}

\vspace{4pt}

\item{\cventry{August 2016 -- June 2018}{www.juniv.edu}{Research Data Scientist}{Jahangirnagar University, Savar, Dhaka}{}{\vspace{3pt}
\begin{itemize}
\item  Assisted full time in 4 research projects in internal coordination \& data collection.  
\item  Conducted proposal writing, developing questionnaire, data collection, data analysis & manuscripts presentation in several conferences.

\end{itemize}
}}



\end{itemize}

\section{EDUCATION}

\vspace{4pt}

\begin{itemize}

\item{\cventry{2019 -- Present}{ Berlin}{Masters in Data Science}{Freie Universität Berlin}{\textit{Germany}}{}}
\begin{itemize}
\item  \textbf{Major Courses:} Statistics for Data Science, Machine Learning for Data Science, Programming for Data Science (Python, C++, Knime), Machine Learning for Bioinformatics, Analysis of Large Data Sets in Bioinformatics, Network Analysis, Natural Language Processing, Data Science Database Systems, Pattern Recognition, Artificial Intelligence. 
\end{itemize}

\vspace{4pt}

\item{\cventry{2011 -- 2016}{Dhaka}{Bachelor in Statistics}{Jagannath University}{\textit{Bangladesh}}{}}
\begin{itemize}
\item  \textbf{Major Courses:} Probability, Numerical Mathematics, Hypothesis, Mathematical Statistics, Calculus, Linear Algebra, Time Series Analysis, Ordinary Differential Equation, Data Analysis with Excel & SPSS, Operations Research, Elementary Estimation Theory, Demography, Stochastic Process, R Programming, Sampling Theory, Design & Experiment, Economics, Regression & Econometrics, Decision Theory & Bayesian Methods, Biostatistics. 
\end{itemize}

\end{itemize}

\vspace{2pt}

\section{TECHNICAL SKILLS}

\vspace{1pt}

\begin{itemize}

\item \textbf{Programming Languages:} Python, R, C++

\vspace{1pt}

\item \textbf{ML Tools:} Numpy, Pandas, SciPy, Scikit-learn, Tensorflow, PyTorch, NLTK, Spacy, KNIME

\vspace{1pt}

\item \textbf{Visualization Tools:} Matplotlib, Seaborn, Plotely, Bokeh

\vspace{1pt}

\item \textbf{Database System:} MySQL, Postgre SQL

\vspace{1pt}

\item \textbf{Big Data Tools:} Apache Spark(PySpark), BigQuery

\vspace{1pt}

\item \textbf{Version Control:} git, Docker

\vspace{1pt}

\item \textbf{Operating System:} Ubuntu, Windows

\end{itemize}

\section{PERSONAL PROJECTS}

\vspace{3pt}

\begin{itemize}

\item  \textbf{Wisconsin Heart Disease Dataset Analysis (Classification)} - Data Preprocessing, Machine Learning(Logistic Regression, SVM, Decision Tree, Naive Bayes, Random Forest), Evaluation. \href{www.firoj.net}{(Github Link)}

\vspace{3pt}

\item \textbf{UCI Healthcare Stroke Dataset Analysis (Classification)} - Data Preprocessing, Exploratory Data Analysis, Machine Learning(Logistic Regression, SVM, Decision Tree, Naive Bayes, Random Forest), Evaluation.

\vspace{3pt}

\item \textbf{Credit Card Fraud Detection Prediction (Classification)} - Exploratory Data Analysis, Data Preprocessing(Imbalancement, Standard Scalar), Machine Learning(Logistic Regression, Random Forest, XGBoost, SVM), Evaluation.

\vspace{3pt}

\item “Evaluating Statistical Forecasting Methods to Forecast Daily Patients Volumes in the Emergency Department- A Case Study of Three Selected Hospitals in Dhaka City”; \textbf{Firoj Ahmmed Patwary}, Azizur Rahman; International Conference on Applied Statistics \textbf{(ICAS-2016)}; ISRT, University of Dhaka, Dhaka, Bangladesh.


\vspace{3pt}

\item “A Fuzzy Modeling Approach for Forecasting Tenualosa ilisha Production in Bangladesh”; \textbf{Firoj Ahmmed Patwary}, Md. Khalid Hossain Shimul, Azizur Rahman; International Conference on Applied Statistics \textbf{(ICAS-2016)}; ISRT, University of Dhaka, Dhaka, Bangladesh.

\end{itemize}


\vspace{2pt}

\section{Langues}

\vspace{1pt}

\begin{itemize}

\item \textbf{English:} Fluent

\vspace{1pt}

\item \textbf{Bengali:} Mother Tongue

\vspace{1pt}

\item \textbf{German:} A1
\vspace{1pt}


\end{itemize}


\nocite{*}
\bibliographystyle{plain}
\bibliography{publications}                       

\end{document}



